ZCB Pricing

### 2018-08-06 ZCB Pricing .Rmd
Fixed Finite Differences

  # Working backwards in time
  for (i in 1:(length(I)+1)){
    C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
    C[M,1] <- (pu(M))*Bond_values[M,1]
    C[1,1] <- pd(1)*Bond_values[1,1]

@@

  for (i in 1:(length(I) +1)){
    C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
    C[M,1] <- (-pu(M))*Bond_values[M,1]
    C[1,1] <- -pd(1)*Bond_values[1,1]

@@

  #========================================================================================
  # Constructing more matricies and iterating the procedure from maturity to time 0

  Bond_values <- matrix(1,nrow = M, ncol = 1)

  # C_2 <- matrix(0,nrow = M,ncol = 1)
  # C_2[1,1] <- pd(1)
  # C_2[M,1] <- pu(M)
  Inv <- solve(Diag_1)

  for (i in 1:(length(I)+1)){
    C_1 <- matrix(0,nrow = M,ncol = 1)
    C_1[1,1] <- pd(1)*Bond_values[1,1]
    C_1[M,1] <- pu(M)*Bond_values[M,1]
    RHS <- Diag_2%*%Bond_values +2*C_1
    Bond_values <- Inv%*%RHS
  }

@@

```{r 10, echo = FALSE}
# Comparison of results for numerical methods

>>>>

  # Working backwards in time
  for (i in 1:(length(I))){
    C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
    C[M,1] <- (pu(M))*Bond_values[M,1]
    C[1,1] <- pd(1)*Bond_values[1,1]

@@

  for (i in 1:(length(I))){
    C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
    C[M,1] <- (-pu(M))*Bond_values[M,1]
    C[1,1] <- -pd(1)*Bond_values[1,1]

@@

  #========================================================================================
  # Constructing more matricies and iterating the procedure from maturity to time 0
  Inv <- solve(Diag_1)

  Bond_values_1 <- matrix(1,nrow = M, ncol = 1)
  Bond_values_2 <- matrix(1,nrow = M, ncol = 1)
  C_1 <- matrix(0,nrow = M,ncol = 1)
  C_1[1,1] <- pd(1)*Bond_values_1[1,1]
  C_1[M,1] <- pu(M)*Bond_values_1[M,1]
  RHS <- Diag_2%*%Bond_values_1 +2*C_1
  Bond_values_1 <- Inv%*%RHS

  for (i in 1:(length(I)-1)){
    C_2 <- matrix(0,nrow = M,ncol = 1)
    C_2[1,1] <- pd(1)*Bond_values_2[1,1]
    C_2[M,1] <- pu(M)*Bond_values_2[1,1]

    C_1 <- matrix(0,nrow = M,ncol = 1)
    C_1[1,1] <- pd(1)*Bond_values_1[1,1]
    C_1[M,1] <- pu(M)*Bond_values_1[M,1]

    RHS <- Diag_2%*%Bond_values_1 + C_1 + C_1
    Bond_values <- Inv%*%RHS
    Bond_values_2 <- Bond_values_1
    Bond_values_1 <- Bond_values
  }

@@

```{r 10}
# Comparison of results for numerical methods
